Social_Isolation_and_Loneliness

### 2023-03-19 FEM_R/Loneliness_Social_Isolation/PAPER_WORKING_SCRIPT.Rmd
Added lots of analysis for the detailed output intervention stuff, as well as generated new populations (and fixed some old ones) in reweight_ELSA_repl.do

@@

```{r}
# Now do change plots starting with the ly.all object
ly.change <- ly.all %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('mean', 'min', 'max', 'margin')) %>%
  mutate(L_change = mean_No_Loneliness - mean_Baseline,
         S_change = mean_No_Social_Isolation - mean_Baseline,
         LS_change = mean_Neither - mean_Baseline,
         L_min = L_change - margin_No_Loneliness,
         L_max = L_change + margin_No_Loneliness,
         S_min = S_change - margin_No_Social_Isolation,
         S_max = S_change + margin_No_Social_Isolation,
         LS_min = LS_change - margin_Neither,
         LS_max = LS_change + margin_Neither) %>%
  pivot_longer(cols = L_change:LS_max,
               names_to = 'scenario',
               values_to = 'LifeYears')

 # %>%
 #  mutate(L_min = L - margin_No_Loneliness,
 #         L_max = L + margin_No_Loneliness,
 #         S_min = S - margin_No_Social_Isolation,
 #         S_max = S + margin_No_Social_Isolation,
 #         LS_min = LS - margin_Neither,
 #         LS_max = LS + margin_Neither)

#ggplot(data = ly.change, aes(x = outcome, y = LifeYears, fill = scenario)) +
  #geom_col(position = 'dodge', stat = 'identity') +
  #geom_errorbar(ymin = (LifeYears - margin), ymax = (LifeYears + margin))
```

@@

>>>>

```{r}
# save these large files in case I overwrite the output stuff
write.csv(cohort, file = 'input_data/detailed_output/cohort_append_large.csv')
write.csv(nolnly, file = 'input_data/detailed_output/nolnly_append_large.csv')
write.csv(nosociso, file = 'input_data/detailed_output/nosociso_append_large.csv')
write.csv(both, file = 'input_data/detailed_output/both_append_large.csv')
```

@@

```{r}
# Now do change plots starting with the ly.all object
ly.change <- ly.all %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('mean', 'min', 'max', 'margin')) %>%
  mutate(L_change = mean_No_Loneliness - mean_Baseline,
         S_change = mean_No_Social_Isolation - mean_Baseline,
         LS_change = mean_Neither - mean_Baseline,
         L_min = L_change - margin_No_Loneliness,
         L_max = L_change + margin_No_Loneliness,
         S_min = S_change - margin_No_Social_Isolation,
         S_max = S_change + margin_No_Social_Isolation,
         LS_min = LS_change - margin_Neither,
         LS_max = LS_change + margin_Neither) %>%
  select(outcome, contains('L_'), contains('S_'), contains('LS_'), -contains('No_Social_Isolation')) %>%
  pivot_longer(cols = L_change:LS_max,
               names_sep = '_',
               names_to = c('scenario', 'statistic'),
               values_to = 'LifeYears') %>%
  pivot_wider(names_from = 'statistic',
              values_from = 'LifeYears')

ly.change$scenario <- factor(ly.change$scenario, levels = c('L', 'S', 'LS'))

combined.plot <- ggplot(data = ly.change, aes(x = scenario, y = change, fill=scenario)) +
  geom_col() +
  facet_wrap(~outcome) +
  geom_errorbar(aes(ymin = min, ymax = max)) +
  labs(title = 'Life Years, Disease Free Life Years, and Disability Free Life Years') +
  xlab('Scenario') +
  ylab('Change (years)')

combined.plot

path <- 'FEM_R/Loneliness_Social_Isolation/plots/'

ggsave(filename = 'ly_dfly_facet_all_confints.png',
      plot = combined.plot,
      path = path,
      width = 9,
      height = 6)
```

### Realistic Intervention

```{r}
lnly.real <- detailed_output_append(base.out.dir = out.dir,
                              scenario = 'ELSA_real_lnly')
lnly.sociso <- detailed_output_append(base.out.dir = out.dir,
                              scenario = 'ELSA_real_sociso')
```

```{r}
ly.lnly.real <- ly_outcomes_from_detailed_output(lnly.real)
ly.sociso.real <- ly_outcomes_from_detailed_output(lnly.sociso)

ly.lnly.real$scenario <- 'Loneliness'
ly.sociso.real$scenario <- 'Social_Isolation'

ly.comb.list <- list(ly.coh, ly.lnly.real, ly.sociso.real)
ly.combined <- do.call(rbind, ly.comb.list)

# arrange columns properly
ly.combined <- ly.combined %>% select(scenario, everything())

ly.combined$scenario <- factor(ly.combined$scenario, levels = c('Baseline', 'Loneliness', 'Social_Isolation'))
ly.combined$outcome <- factor(ly.combined$outcome, levels = c('LY', 'DiseaseFLY', 'DisabilityFLY'))
```

#### LY & DFLYs
```{r}
ly.ly <- ly.combined %>% 
  filter(outcome == 'LY') %>%
  select(-outcome)

ly.disease <- ly.combined %>%
  filter(outcome == 'DiseaseFLY') %>%
  select(-outcome)

ly.disability <- ly.combined %>%
  filter(outcome == 'DisabilityFLY') %>%
  select(-outcome)

Now change plots.

```{r}
# Now do change plots starting with the ly.all object
ly.change.real <- ly.combined %>%
  pivot_wider(names_from = 'scenario',
              values_from = c('mean', 'min', 'max', 'margin')) %>%
  mutate(L_change = mean_Loneliness - mean_Baseline,
         S_change = mean_Social_Isolation - mean_Baseline,
         L_min = L_change - margin_Loneliness,
         L_max = L_change + margin_Loneliness,
         S_min = S_change - margin_Social_Isolation,
         S_max = S_change + margin_Social_Isolation) %>%
  select(outcome, contains('L_'), contains('S_')) %>%
  pivot_longer(cols = L_change:S_max,
               names_sep = '_',
               names_to = c('scenario', 'statistic'),
               values_to = 'LifeYears') %>%
  pivot_wider(names_from = 'statistic',
              values_from = 'LifeYears')

ly.change.real$scenario <- factor(ly.change.real$scenario, levels = c('L', 'S', 'LS'))

combined.plot <- ggplot(data = ly.change.real, aes(x = scenario, y = change, fill=scenario)) +
  geom_col() +
  facet_wrap(~outcome) +
  geom_errorbar(aes(ymin = min, ymax = max)) +
  labs(title = 'Life Years, Disease Free Life Years, and Disability Free Life Years') +
  xlab('Scenario') +
  ylab('Change (years)')

combined.plot
```

@@

As a first step, lets get the breakdown by gender and age group of loneliness and social isolation (for planning interventions).

```{r}
lnly.check <- repl %>%
  select(hhidpn, year, age, male, lnly) %>%
  filter(year == 2012) %>%
  group_by(lnly, male) %>%
  count()

lnly.check2 <- repl %>%
  filter(year == 2012) %>%
  select(male, lnly) %>%
  group_by(lnly) %>%
  summarise(n = n(),
            male = sum(male) / n,
            female = 1 - male)

lnly.check3 <- long %>%
  select(male, lnly) %>%
  group_by(lnly) %>%
  summarise(n = n(),
            male = sum(male) / n,
            female = 1 - male)

lnly.check4 <- stock %>%
  select(male, lnly) %>%
  group_by(lnly) %>%
  summarise(n = n(),
            male = sum(male) / n,
            female = 1 - male)

lnly.check5 <- repl %>%
  filter(year == 2012) %>%
  select(hhidpn, year, age, male, childless, lnly) %>%
  group_by(lnly, male, childless) %>%
  count()
```
